Clicks and Cliques

### 2018-12-18 papersoul.Rnw
tidy corplot chunck

<<missing, echo=FALSE,dependson= 'data',results='asis'>>=
miss <- is.na(soul)
# Percentage per Case (1) and per variable (2)
tab1 <- cbind(quantile(apply(miss[,orig], 1, mean) ),
            quantile(apply(miss[,reco], 1, mean)),
            quantile(apply(miss[,orig], 2, mean) ),
            quantile(apply(miss[,reco], 2, mean) ) )

@@

aux <- census.data %>% filter( QSB %in% grps ) %>%
  mutate(gr =factor(c(2, 1, 2, 2, 3, 3, 3, 1, 1, 3, 2)), h1 = c(1, 0, 0, 0, 1, 1, 1, 0, 0, 0, 1), v1 = c(0, 0, 0, 1, 0, 1, 0, 0, 0, 0, 0),
         h2 = c(0, 1, 0, 1, 0, 0, 0, 0, 0, 0, 1), v2 = c(0, 0, 1, 0, 0, 1, 0, 0, 0, 0, 0))

ggplot(census.data, aes(gini, income.pc)) + geom_point(size = I(4)) + geom_text(data = aux, aes(gini,income.pc, label = QSB, color = gr, hjust = h1,vjust = v1), size = I(6)) + ylab('Income per capita') + xlab('Gini') + theme(legend.position = "none")

ggplot(census.data, aes(Bachelor.s.degree.or.higher., income.pc)) + geom_point(size = I(4)) +  geom_text(data = aux, aes(Bachelor.s.degree.or.higher.,income.pc, label = QSB, color = gr, hjust = h2, vjust = v2), size = I(5))  + ylab('Income per capita') + xlab('Bachelor Degree') + theme(legend.position = "none")
@
\caption{Scatter plot of income per capita by Gini index (left) and scatter-plot of income per capita by proportion of people with bachelor degree (right). Colors identify some groups based on income and Gini. \label{ecolink}}
\end{figure}

@@

\begin{figure}[hbpt]
<<cluster.cen, dependson=c('data','corplot'), echo=FALSE,message=FALSE,warning=FALSE>>=
var.cl2 <- colnames(census.data) %in% c("aveageF","prop1821", "Bachelor.s.degree.or.higher." , "gini" , "own.rate" , "afri.prop",'prop.new.entry','un.rate',"prop.no.workers" )
d2 <- dist(census.data[, var.cl2])
hc2 <- hclust(d2, method = 'ward.D')
census.data$cl.2 <- cutree(hc2,4)

@@

census.data %>% select( c(colnames(census.data)[var.cl2],'cl.2' ) ) %>% 
  group_by(cl.2) %>%
  summarise_all(funs(mean)) %>%
  setNames(nn) %>% ungroup() %>%
  mutate(cl.2 = factor(cl.2)) %>%
  ggparcoord(columns = 2:10, scale = 'std', 
             groupColumn = 'cl.2', showPoints = T, 
             order = c(3, 4, 6, 10, 2, 5, 9, 7, 8))  + 
  theme(axis.text.x = element_text(angle = 90, size = I(15))) + 
  xlab('') + ylab('') + 
  scale_color_brewer(type = 'qual', palette = 2, name = 'Group')
@
\caption{Parallel coordinate plot for community cluster means. \label{cluster.cen} }
\end{figure}

@@

# cors1 <- cor(x = census.data[, 2:63], y = census.data[, 64])
# cors2 <- cor(x = census.data[, 2:63], y = census.data[, 65])
# nm <- names(cors1[ rank(cors1) %in% c(1:10, 53:62), ])
# dat.cor <- rbind(
# data.frame(vars = rownames(cors1), cor = cors1[,1], positive = cors1[,1]>0, type = 'Attached') ,
# data.frame(vars = rownames(cors2), cor = cors2[,1], positive = cors2[,1]>0, type = 'Not Attached') )
# dat.cor2 <- subset(dat.cor, vars %in% nm)
# dat.cor2$vars <- reorder(factor(dat.cor2$vars), (dat.cor2$cor) *(dat.cor2$type=='Attached'), mean)

cors <- census.data.new %>% 
  gather(vars, vv, -QSB, -CCEGRP2Attached, -`CCEGRP2Not Attached` ) %>%
  group_by(vars) %>% 
  summarise(
    cor.att = cor(vv, CCEGRP2Attached, use = 'complete.obs'),
    cor.noatt = cor(vv, `CCEGRP2Not Attached`, use = 'complete.obs') ) %>% 
  filter(!is.na(cor.att), vars != 'unemployed') %>% 
  filter(rank(cor.att) %in% c(1:10, 52:61) ) %>% 
  mutate(vars =  fct_reorder(vars, cor.att) ) %>% 
  gather(type, vv, -vars) %>% 
  mutate( type = factor(type, labels=c('Attached', 'Not Attached') ),
          positive = factor(sign(vv), labels=c( 'Negative', 'Positive') ) )

levels(dat.cor2$vars) <-  c('Aver.years.own.in.community','size.community','Average.years.rent.in.community','Prop.owner.more.10.years','Pro.female','Prop.house.2.per.1.worker','Prop.house.4.per.or.more','Prop.rent.more.10.years','Prop.own','Unemployment.rate','Prop.1worker','Prop.bachelor','Prop.house.3.per.3.workers','Prop.native.entry.90s','Prop.native.entry.80s','Prop.militar','Prop.pop.bw.18.21','Prop.new.entry','Prop.male','Prop.2perhouse')

dat.cor2$positive <- factor(dat.cor2$positive)
levels(dat.cor2$positive) <- c('Negative','Positive')

qplot(data = dat.cor2, y = vars, x = cor, xlab = 'Correlation', ylab = '', color = positive, facets =~type, size = I(3)) + theme(legend.position= 'bottom', legend.title = element_blank(), axis.text.y = element_text(size = I(15)))

# cors %>% 
#   ggplot() + 
#   geom_point(aes(y = vars, x=vv, color = positive)) +
#   facet_grid(~type)

>>>>

<<missing, echo=FALSE,dependson= 'data',results='asis'>>=
miss <- data.frame(is.na(soul))
# Percentage per Case (1) and per variable (2)

tab1 <- cbind(quantile(apply(miss[,orig], 1, mean) ),
            quantile(apply(miss[,reco], 1, mean)),
            quantile(apply(miss[,orig], 2, mean) ),
            quantile(apply(miss[,reco], 2, mean) ) )

@@

aux <- census.data %>% filter( QSB %in% grps ) %>%
  mutate(gr = factor(c(2, 1, 2, 2, 3, 3, 3, 1, 1, 3, 2)),
         h1 = c(1, 0, 0, 0, 1, 1, 1, 0, 0, 0, 1), 
         v1 = c(0, 0, 0, 1, 0, 1, 0, 0, 0, 0, 0),
         h2 = c(0, 1, 0, 1, 0, 0, 0, 0, 0, 0, 1),
         v2 = c(0, 0, 1, 0, 0, 1, 0, 0, 0, 0, 0))

ggplot(census.data, aes(gini, income.pc)) + 
  geom_point(size = I(4)) + 
  geom_text(data = aux, aes(gini,income.pc, label = QSB, color = gr, hjust = h1, vjust = v1), size = I(6)) + 
  labs(y = 'Income per capita', x ='Gini') +
  theme(legend.position = "none")

ggplot(census.data, aes(Bachelor.s.degree.or.higher., income.pc)) + 
  geom_point(size = I(4)) +  
  geom_text(data = aux, aes(Bachelor.s.degree.or.higher.,income.pc, label = QSB, color = gr, hjust = h2, vjust = v2), size = I(5))  + 
  labs(y = 'Income per capita', x = 'Bachelor Degree') + 
  theme(legend.position = "none")
@
\caption{Scatter plot of income per capita by Gini index (left) and scatter-plot of income per capita by proportion of people with bachelor degree (right). Colors identify some groups based on income and Gini. \label{ecolink}}
\end{figure}

@@

\begin{figure}[hbpt]
<<cluster.cen, dependson=c('data','corplot'), echo=FALSE,message=FALSE,warning=FALSE>>=
# var.cl2 <- colnames(census.data) %in% c("aveageF","prop1821", "Bachelor.s.degree.or.higher." , "gini" , "own.rate" , "afri.prop",'prop.new.entry','un.rate',"prop.no.workers" )
d2 <- census.data %>% select(aveageF, prop1821, Bachelor.s.degree.or.higher., gini , own.rate , afri.prop, prop.new.entry, un.rate, prop.no.workers ) %>% dist()

# d2 <- dist(census.data[, var.cl2])
hc2 <- hclust(d2, method = 'ward.D')
# census.data$cl.2 <- cutree(hc2, 4)

@@

census.data %>%
  mutate(cl.2 = cutree(hc2, 4) ) %>% 
  select( c(colnames(census.data)[var.cl2],'cl.2' ) ) %>% 
  group_by(cl.2) %>%
  summarise_all(funs(mean)) %>%
  setNames(nn) %>% ungroup() %>%
  mutate(cl.2 = factor(cl.2)) %>% 
  ggparcoord(columns = 2:10, scale = 'std', 
             groupColumn = 'cl.2', showPoints = T, 
             order = c(4, 10, 2, 7, 8, 6, 3,5, 9))  + 
  theme(axis.text.x = element_text(angle = 90, size = I(15))) + 
  labs(x = '', y = '') + 
  scale_color_brewer(type = 'qual', palette = 2, name = 'Group')

  # c(3, 4, 6, 10, 2, 5, 9, 7, 8)
@
\caption{Parallel coordinate plot for community cluster means. \label{cluster.cen} }
\end{figure}

@@

cors <- census.data %>% 
  gather(vars, vv, -QSB, -CCEGRP2Attached, -`CCEGRP2Not Attached` ) %>%
  group_by(vars) %>% 
  summarise(
    cor.att = cor(vv, CCEGRP2Attached, use = 'complete.obs'),
    cor.noatt = cor(vv, `CCEGRP2Not Attached`, use = 'complete.obs') ) %>% 
  filter(!is.na(cor.att), vars != 'unemployed') %>% 
  filter(rank(cor.att) %in% c(1:10, 52:61) ) %>% 
  mutate(vars =  fct_reorder(vars, cor.att) , vars = recode_factor(
      vars, 
      "av.own" = 'Aver.years.own.in.community',
      "pop100"= 'size.community', 
      "av.rent"= 'Average.years.rent.in.community',
      "ow.prop10" = 'Prop.owner.more.10.years',
      "prop.female" = 'Pro.female',
      "prop2.1worker" = 'Prop.house.2.per.1.worker',
      "prop.4.per" = 'Prop.house.4.per.or.more',
      "ren.prop10" = 'Prop.rent.more.10.years',
      "own.rate" = 'Prop.own',
      "un.rate" = 'Unemployment.rate',
      "prop1.worker" = 'Prop.1worker',
      "Bachelor.s.degree.or.higher." = 'Prop.bachelor',
      "prop3.3worker" = 'Prop.house.3.per.3.workers',
      "prop.nat.entry.90s" = 'Prop.native.entry.90s',
      "prop.nat.entry.80s" = 'Prop.native.entry.80s',
      "militar" = 'Prop.militar',
      "prop1821" = 'Prop.pop.bw.18.21',
      "prop.entry.80s" = 'Prop.new.entry',
      "prop.male" = 'Prop.male',
      "prop.2.per" = 'Prop.2perhouse')) %>% 
  gather(type, vv, -vars) %>% 
  mutate( type = factor(type, labels = c('Attached', 'Not Attached') ),
          positive = factor(sign(vv), labels = c( 'Negative', 'Positive') ) )

cors %>%
  ggplot() +
  geom_point(aes(y = vars, x = vv, color = positive), size = I(3)) +
  facet_grid(~type) + theme(legend.position = 'bottom', legend.title = element_blank(), axis.text.y = element_text(size = I(15))) + labs(y = "", x = "Correlation")
